---
title: "FARS Data Analysis"
author: "Raedler, Patrick"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS Data Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Reading, Summarizing and Visualizing FARS Data

## Description

The functions in this package will enable the user to read, summarize, and visualize Fatalaty Analysis Recording System (FARS)
data. FARS data will need to be stored in the workin directory in the "accident_year.csv.bz2" format, where "year" will be a 
specific year for which data was recorded.  

## Usage

-- make_filename(year)  
-- fars_read(filename)  
-- fars_read_years(years)  
-- fars_summarize_years(years)  
-- fars_map_state(state.num, year)  

## Arguments 

filename    Name of the FARS file stored in the working directory  
state.num   The number of a state that is to be mapped (From 1 to 51)  
year        Year for which the FARS data wants to be assesed (e.g 2013)
years       One or multiple years that correspond to FARS files for that/those year/s  

## **Examples**
```{r dplyr, echo=FALSE, message=FALSE}
library(dplyr)
library(readr)
library(FarsPackageCoursera)
library(tidyr)
library(maps)
library(graphics)

```

To make the **filename**:
```{r make_filename, echo=TRUE}
make_filename(2013)
```

To **read** in the FARS file from the working directory:
```{r fars_read_1, eval=FALSE}
fars_read("accident_2013.csv.bz2")
```
or:
```{r fars_read_2, eval=FALSE}
fars_read(make_filename(2013))
```

**Reads** accident file and **returns** tibble with month and year:
```{r fars_read_years, eval=TRUE}
fars_read_years(2013)
```

**Returns** the number of accidents per month of select years:
```{r fars_summarize_years}
fars_summarize_years(2013)
```

**Graphs** accident locations on US state maps
```{r fars_map_state, fig.show='hold'}
fars_map_state(23, 2013)
fars_map_state(29, 2013)
```

## Notes

This package requires the FARS files to be in the format created by *make_filename*. If these files are not in this required format all other functions in this package will result in an error.  
